Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii–Moriya interactions in antiferromagnetic insulators

### 2019-01-29 Paper/paper.tex
Introduce disorder to paper

\begin{align}
\label{MKMH}
\hat{H}_0 &= - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \n \\
	&+\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 + i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
	\text{U}\hat{D}
\end{align}

@@

>>>>

\begin{align}
\label{MKMH}
\hat{H}_0 &= - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \n \\
	&-\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 - i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
	\text{U}\hat{D}
\end{align}

@@

\begin{subsection}{Disorder}
It is possible to introduce the effect of disorder in the model \ref{MKMH} by adding random uncorrelated on-site energies:

\begin{align}
\label{DisorderedHubbardModel}
\hat{H}_0 &= - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} -\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 - i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \n \\
	& + \sum_{i \sigma} \epsilon_i \hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma} +
	\text{U}\hat{D}
\end{align}

Where $\epsilon_i$ are uncorrelated random variables $\epsilon_i \in [-W,W]$. At half filling we can derive an effective Hamiltonian using the same procedure as before. The second order virtual hopping $i\sigma \rightarrow j\sigma \rightarrow i\sigma$ will give rise to an exchange spin interaction. In this case, however, the intermediate energy is $\text{U} + (\epsilon_j - \epsilon_i)$. Therefore the spin Hamiltonian will be:

\begin{align}
&\hat{H}_{\text{eff}}^{\text{Dis}} = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\bs{S}_j +\n \\
&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
\end{align}

With:

\begin{align*}
J_{1,ij} &= \frac{2t_1^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \\
J_{2,ij} &= \frac{2t_2^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \\
\bs{D}_{2,ij} &= -\frac{4\nu_{ij} t_2 \Delta \text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}\hat{e}_z \\
\bs{\Gamma}_{2,ij} &= \frac{2\Delta^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}\text{diag}(-1,-1,1)
\end{align*}

Where in the second step we added the contributions of $\langle i,j \rangle$ and $\langle j,i \rangle$ and where $J_{ij} = \frac{2t^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}$. This model is relevant for studying many-body localization phenomena \cite{Protopopov}.
\end{subsection}
